\sysfull

### 2017-08-09 paper/paper.tex
Asbtract swiftly rewritten - ready for Brandon
added some edits to section 2.  still needs  alot, especially in the task section
remove iposDataProtection reference from main file
done with an aggressive pass over compiler
Placeholder for Conclusions (will require Brandon's hand and eye later)
Background section revised (yaay)
patched wrong section label
Revisions of virtualization section
Section I revised
title edit

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{tikz}
\usepackage{listings}
\usepackage{flushend}

@@

\newcommand{\sys}{VIPE\xspace}

%Title Options
%\newcommand{\sysfull}{VIPER: Virtualised Intermittent Programming model, Execution model, and Runtime environment}
%\newcommand{\sysfull}{VIPER: Virtualized Intermittently-Powered Execution Runtime}
%\newcommand{\sysfull}{PREVIEW: Programming and Runtime Environment with Virtualised Intermittent Execution Windows}
%\newcommand{\sysfull}{VIPE: Virtualized Intermittently-Powered Execution}
\newcommand{\sysfull}{VIPER: Virtual Intermittently-Powered Execution on the Run}

@@

\section{\sysfull}
\label{sec:overeall_system}

@@

\section{Compiler Support for Automatic Task Generation}
\label{sec:compiler}

@@

\input{iposdataprotection}

\section{Memory Virtualization}
\label{sec:memory_virtulaization}

@@

\section{Task Coalescing}
\label{sec:task_coalescing}

@@

\section{Conclusions}
\label{sec:conclusions}

>>>>

\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{tikz}
\usepackage{listings}
%Brandon: this broke the build for me
%\usepackage[keeplastbox]{flushend}

\hypersetup{colorlinks=false,linkcolor=blue,urlcolor=blue}
\urlstyle{rm}

@@

\newcommand{\sys}{Coala\xspace}
\newcommand{\transition}{{\tt next\_task}\xspace}

%Title Options (Brandon: your call which one)
%\newcommand{\sysfull}{VIPER: Virtualised Intermittent Programming model, Execution model, and Runtime environment}
%\newcommand{\sysfull}{VIPER: Virtualized Intermittently-Powered Execution Runtime}
%\newcommand{\sysfull}{PREVIEW: Programming and Runtime Environment with Virtualised Intermittent Execution Windows}
%\newcommand{\sysfull}{VIPE: Virtualized Intermittently-Powered Execution}
\newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Execution with Adaptive Coalescing and Memory Virtualization}

@@

\section{\sysfull}
\label{sec:overall_system}

@@

\section{\sys Automatic Task Generation}
\label{sec:compiler}

@@

\section{\sys Memory Virtualization}
\label{sec:memory_virtulaization}

@@

\section{\sys Task Coalescing}
\label{sec:task_coalescing}

@@

\section{Conclusions and Future Work}
\label{sec:conclusions}
